---
title: "Cake Data Analysis"
output: html_notebook
---

###### 1.2.2 Analysis questions




## Loading packages
```{r}
library(tidyverse)
library(dplyr)
library(janitor)
library(tidyr)
library(here)
```



## Loading in csv file of cleaned data.

```{r}
cake_ingredients_data <- read_csv(here("clean_data/cake_ingredients_clean.csv"))
```


## Question 1. Which cake has the most cocoa in it?

```{r}
cake_ingredients_data %>%
  filter(ingredient == "Cocoa")

```



## Question 2. For sponge cake, how many cups of ingredients are used in total?
```{r}
ingredient_cups <- cake_ingredients_data %>%
  filter(cake == "Sponge", measure == "cup") %>%
  group_by(measure == "cup") %>%
  count(amount_of_measure)
  
ingredient_cups_2 <- ingredient_cups %>%
  mutate(total = amount_of_measure * n, na.rm=TRUE)


sum(ingredient_cups_2$total)


```
## The number of cups of ingredients used is 3.5.


## Question 3. How many ingredients are measured in teaspoons?

```{r}
cake_group <- cake_ingredients_data %>% 
  filter(measure == "teaspoon", amount_of_measure > 0) %>%
  group_by("ingredient")

unique(cake_group$ingredient)
```
## Eight ingredients are measured in teaspoons.
 



## Question 4. Which cake has the most unique ingredients?

```{r}

cake_unique <- cake_ingredients_data %>% 
  filter(amount_of_measure > 0)

table(cake_unique$cake)


```


## Question 5. Which ingredients are used only once?

```{r}
ingredient_count <- cake_ingredients_data %>%
  filter(amount_of_measure > 0)
  
table(ingredient_count$ingredient)
```
## Bananas, Cream of tartar, Crushed Ice, Dried Currants, Egg white, Nutmeg, Nuts, Zwiebach are used once.
